VIPRE: Virtualized Intermittently-Powered Runtime Environment

### 2017-07-11 paper/background.tex
Expanding background section

\begin{table}
	\begin{tabular}{|c|c|}
	\hline
	Platform Name & Storage capacitor size \\
	\hline \hline
	NeuralWISP~\cite{} & 100\,$\mu$F \\
	BioImpedance~\cite{} & 20\,$\mu$F \\
	WISPCam~\cite{} & 6.08\,mF \\ %tested [11.24, 17.45, 21.98]\,mF
	NFC-WISP~\cite{zhao_rfid_2015} & 300\,$\mu$F \\
	WISP~\cite{} & 47\,$\mu$F \\
	\hline
	\end{tabular} 
\caption{Comparison of storage sizes for various battery-less platforms.}
\label{table:capacitor}
\end{table}

@@

We can write the problem formally as
%
\begin{equation}
\underset{i}{\arg\,\min} \sum_{i}m_i+t_i \text{~subject to~} \forall_i mi+t_i>e
\end{equation}

>>>>

\begin{table}
	\begin{tabular}{|c|c|}
	\hline
	Platform name & Storage capacitor size \\
	\hline \hline
	NeuralWISP~\cite{holleman_biocas_2008} & 100\,$\mu$F \\
	BioImpedance~\cite{rodriguez_tbcs_2015} & 20\,$\mu$F \\
	WISPCam~\cite{naderiparizi_rfid_2015} & 6.08\,mF \\ %tested [11.24, 17.45, 21.98]\,mF
	NFC-WISP~\cite{zhao_rfid_2015} & 300\,$\mu$F \\
	Moo~\cite{moo} & X\,$mu$F \\
	WISP~\cite{wisp5} & 47\,$\mu$F \\
	X~\cite{nadeau_naturebio_2017}~\cite{} & X\,$mu$F\\
	\hline
	\end{tabular} 
\caption{Comparison of storage sizes for various battery-less platforms. Values for other representative platforms~\cite{medusa_farsens_2017,talla_imwut_2017,liu_sigcomm_2013,parks_sigcomm_2014} were not reported in their respective papers.}
\label{table:capacitor}
\end{table}

@@

We can write the problem of maximizing all task sizes formally as
%
\begin{equation}
\underset{i}{\arg\,\max} \sum_{i}m_i+t_i \text{~subject to~} \forall_i mi+t_i>e,
\end{equation}
%
where $e$ is the required minimum energy to perform a task, $i$ is the total number of tasks, $m_i$ and $t_i$ are the cost of task traversal (memory copying time of task variables) and time to complete one task, respectively.
